Microstim: open source hardware for precise electrical stimulation

### 2019-02-25 benchmarking/paper/draft0.Rmd
boatload of updates via jons suggestions. de-isolated grounds via large resistors+capacitors (to prevent static buildup on animal or issues with large discharges). increased resistor values in voltage output non-inverting amplifier.

    plot(x[1:3000], type='l', ylim=c(190,220))
    points(pulseIndices, x[pulseIndices], cex=0.3, col='red')
    points(pulseStartIndices, x[pulseStartIndices], cex=1, col='blue')
    points(pulseEndIndices, x[pulseEndIndices], cex=1, col='orange')

@@

    list(IPI.summary=IPI.summary, IPI.sd=IPI.sd, PW.summary=PW.summary, 
             PW.sd=PW.sd, sh.median=sh.median, sh.sd=sh.sd, 
             sl.median=sl.median, sl.sd=sl.sd)
  })
}

@@

par(mar=c(4,5,2,2), mfrow=c(4,3))
plot(sapply(res, function(x) x$IPI.summary[3])*1e6, ylab='Median interpulse interval\n(microsec)')
abline(h=2*unique(paramMat$period), col='red')
plot(sapply(res, function(x) x$IPI.sd)*1e6, ylab='Interpulse interval stdev\n(microsec)')
abline(h=0.5)
plot(sapply(res, function(x) diff(x$IPI.summary[c(1,6)]))*1e6, ylab='Interpulse interval range\n(microsec)')
abline(h=0.5)

plot(sapply(res, function(x) x$PW.summary[3])*1e6, ylab='Median pulse width\n(microsec)')
abline(h=2*unique(paramMat$dur0), col='red')
plot(sapply(res, function(x) x$PW.sd)*1e6, ylab='Pulse width stdev\n(microsec)')
abline(h=0.5)
plot(sapply(res, function(x) diff(x$PW.summary[c(1,6)]))*1e6, ylab='Pulse width range\n(microsec)')
abline(h=0.5)

@@

## Microstim is digital and highly configurable

>>>>

    #plot(x[1:3000], type='l', ylim=c(190,220))
    #points(pulseIndices, x[pulseIndices], cex=0.3, col='red')
    #points(pulseStartIndices, x[pulseStartIndices], cex=1, col='blue')
    #points(pulseEndIndices, x[pulseEndIndices], cex=1, col='orange')

@@

    pulseMat = sapply(pulseStartIndices, function(j) x[j+(-100:1000)])
    list(IPI.summary=IPI.summary, IPI.sd=IPI.sd, PW.summary=PW.summary, 
             PW.sd=PW.sd, sh.median=sh.median, sh.sd=sh.sd, 
             sl.median=sl.median, sl.sd=sl.sd, pulseMat=pulseMat)
  })
}

@@

par(mar=c(4,5,2,2), mfrow=c(4,3))
plot(sapply(res, function(x) x$IPI.summary[3])*1e6, ylab='Median interpulse interval\n(microsec)', log='y')
abline(h=unique(paramMat$period), col='red')
plot(sapply(res, function(x) x$IPI.sd)*1e6, ylab='Interpulse interval stdev\n(microsec)')
abline(h=0.5)
plot(sapply(res, function(x) diff(x$IPI.summary[c(1,6)]))*1e6, ylab='Interpulse interval range\n(microsec)')
abline(h=0.5)

plot(sapply(res, function(x) x$PW.summary[3])*1e6, ylab='Median pulse width\n(microsec)', log='y')
abline(h=2*unique(paramMat$dur0), col='red')
plot(sapply(res, function(x) x$PW.sd)*1e6, ylab='Pulse width stdev\n(microsec)')
abline(h=0.5)
plot(sapply(res, function(x) diff(x$PW.summary[c(1,6)]))*1e6, ylab='Pulse width range\n(microsec)')
abline(h=0.5)

@@

```{r fuckit}

par(mfrow=c(3,3), mar=c(0,0,0,0))
for (i in 1:10){#(length(res)/2)){
  plot(rowMeans(res[[2*i-1]]$pulseMat), type='l', col='black', axes=FALSE, lty=1)
  lines(rowMeans(res[[2*i]]$pulseMat), type='l', col='red', lty=1)
}
```
## Microstim is digital and highly configurable
